---
title: "CovRegFC Workflow"
author: "Christof Seiler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this vignette we go through an entire workflow with real data. We will show how to jointly predict univariate channels brain activity and functional connectivity from experimental conditions. We use the covariance regression model first introduced by Hoff and Niu^[Hoff and Niu (2012), A Covariance Regression Model, Statistica Sinica.].

```{r}
library(CovRegFC)
library(devtools)
library(rprojroot)
library(ggplot2)
library(stringr)
library(R.matlab)
```

## Load Data

This data is open access and available from [here](http://doc.ml.tu-berlin.de/hBCI/). We reshape the data and lead it here now.

```{r}
path = find_package_root_file("vignettes", "data_prepared.Rdata")
load(path)
str(data_prepared)
```

Define response variables. Can be either regions or channels. Possible channel types are:

* For regional oxy: 'oxy'
* For reginoal deoxy: 'deoxy'
* For channel oxy: 'highWL'
* For channel deoxy: 'lowWL'

```{r}
channel_type = "oxy"
var_ids = NULL
if(str_detect(channel_type,"oxy")) {
  var_ids = str_detect(names(data_prepared),paste0("_",channel_type)) %>% which
} else if(str_detect(channel_type,"WL")) {
  frontal = c('AF7Fp1','AF3Fp1','AF3AFz','FpzFp1','FpzAFz','FpzFp2','AF4AFz','AF4Fp2','AF8Fp2')
  motor_left = c('C5CP5','C5FC5','C5C3','FC3FC5','FC3C3','FC3FC1','CP3CP5','CP3C3','CP3CP1','C1C3','C1FC1','C1CP1')
  motor_right = c('C2FC2','C2CP2','C2C4','FC4FC2','FC4C4','FC4FC6','CP4CP6','CP4CP2','CP4C4','C6CP6','C6C4','C6FC6')
  occipital = c('OzPOz','OzO1','OzO2')
  region_list = list(frontal,motor_left,motor_right,occipital)
  channel_names_reorderd = paste0(unlist(region_list),channel_type)
  var_ids = sapply(channel_names_reorderd,function(name) {
    names(data_prepared) %in% name %>% which
  })
}
```

Plot channels.

```{r}
path = find_package_root_file("vignettes", "mnt.mat")
mnt = readMat(path)
channel_location = data.frame(names = mnt$mnt[,,1]$clab %>% unlist,
                              x = mnt$mnt[,,1]$x,
                              y = mnt$mnt[,,1]$y)
channel_location$names = as.character(channel_location$names)
plot_channels(channel_location,
              x_label = "left <--> right",
              y_label = "posterior <--> anterior")
```

Subset data to one the two experiments and channels/regions.

```{r}
# motor task
#data = subset(data_prepared,task == "LMI" | task == "RMI") %>% droplevels
# mental arithmetic task
data = subset(data_prepared,task == "BL" | task == "MA") %>% droplevels
response = names(data)[var_ids]
response
```

## Fit Covariance Model

We can turn around regression model and have the experimental conditions be the explantory variables and the protein expression level be the response variable. We can account for correlation between the error terms of the multivariate response variable using covariance regression model. This model is very similar to "seemingly unrelated regressions" (see Zellner^[Zellner (1962), An efficient method of estimating seemingly unrelated regression equations and tests for aggregation bias, JASA.] and Greene^[Greene (2011), Econometric Analysis.]) with an additional random effects term.

```{r}
condition = "task"
data_subset = data[data$participant %in% 1:10,] %>%
  subset(.,session == 2) %>%
  droplevels
fit_vb = covreg(data_subset,response,condition)
```

Analyze posterior covariance **unexplained** by simulation conditions.

```{r fig.height=4,fig.width=7}
plot_unexplained_cov(fit_vb,response)
```

Analyze posterior covariance **explained** by simulation conditions.

```{r}
plot_explained_cov(fit_vb,data_subset,response,condition)
```

## Session Info

```{r}
session_info()
```
